Job Demands-Resources model components through the lens of O*NET classifications

### 2023-01-17 Submission.Rmd
freeze glitch changes

```{r litresources, fig.cap="Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support."}

###############################################
###############################################

@@

ggplot(summarized, aes(x=category, y=mean, fill=RD)) + geom_bar(stat="identity", position=position_dodge()) + theme_bw() + xlab("") + ylab("Average Job Characteristic Rating") + coord_cartesian(ylim=c(1,5)) + scale_fill_brewer(palette="Blues") + 
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.5, size=0.8, position=position_dodge(.9))

@@

We used 98 statements taken from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3). We retained 41 work activity classifications which O\*NET groups into categories of information input (5 statements), interacting with others (17 statements), mental processes (10 statements) and work output (9 statements). Fifty-seven work context statements grouped into interpersonal relationships (14 statements), physical work conditions (30 statements), and structural job characteristics (13 statements).

@@

> Maybe just do a histogram of standard deviations (overall) or perhaps also by O\*Net dimensions (aim to do this 12/21 in St. Cloud)

@@

> Maybe just put correlations in here - SIOP matrix (challenge, hindrance, resource) - would be most interesting by O\*Net dimension.

@@

> New graph presents these but need an inferential - maybe ANOVAs

@@

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                  caption = "Challenge, hindrance, and resource bivariate correlations.",
                  escape = FALSE, 
                  font_size = "small", 
                  landscape = TRUE)
```

>>>>

```{r litresources}

###############################################
############################################### include & eval=FALSE on 1/16/23 because of new figure which replaced this older attempt

### ACTUALLY, just commented out the graph because other code chunks needed for subsequent commands - 1/17/23 , fig.cap="Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support."

@@

#ggplot(summarized, aes(x=category, y=mean, fill=RD)) + geom_bar(stat="identity", position=position_dodge()) + theme_bw() + xlab("") + ylab("Average Job Characteristic Rating") + coord_cartesian(ylim=c(1,5)) + scale_fill_brewer(palette="Blues") + 
#  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.5, size=0.8, position=position_dodge(.9))

@@

We used 98 statements taken from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3). We retained 41 work activity classifications which O\*NET groups into categories of information input (5 statements; Where and how are the information and data gained that are needed to perform this job?), interacting with others (17 statements; What interactions with other persons or supervisory activities occur while performing this job?), mental processes (10 statements; What processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (9 statements; What physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Fifty-seven work context statements grouped into interpersonal relationships (14 statements; This category describes the context of the job in terms of human interaction processes), physical work conditions (30 statements; This category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (13 statements; This category involves the relationships or interactions between the worker and the structural characteristics of the job).

@@

> Done - Figure \@ref(fig:overallhist)

> NOT DONE: Combine current graphs 2 $\rightarrow$ 8 into only 2 graphs (put resources, challenges, and demands on same graph; Kulas do this)

@@

> Done (at O\*Net dimension level) - Table \@ref(tab:cortab).

@@

> Alicia can you present "what this means" and what is being presented in Figure \@ref(fig:scalelevelgraphs) more clearly - also possibly add ANOVAs

@@

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                  caption = "Challenge, hindrance, and resource bivariate correlations.",
                  escape = FALSE, 
                  font_size = "small", 
                  landscape = TRUE,
                  note = "The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
```

### 2023-01-17 Submission.tex
correlations (big table in as placeholder for now)
freeze glitch changes

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/litresources-1.pdf}
\caption{\label{fig:litresources}Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support.}
\end{figure}

@@

We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}. We retained 41 work activity classifications which O*NET groups into categories of information input (5 statements), interacting with others (17 statements), mental processes (10 statements) and work output (9 statements). Fifty-seven work context statements grouped into interpersonal relationships (14 statements), physical work conditions (30 statements), and structural job characteristics (13 statements).

@@

\begin{quote}
Maybe just do a histogram of standard deviations (overall) or perhaps also by O*Net dimensions (aim to do this 12/21 in St.~Cloud)
\end{quote}

@@

\begin{quote}
Maybe just put correlations in here - SIOP matrix (challenge, hindrance, resource) - would be most interesting by O*Net dimension.
\end{quote}

@@

\begin{quote}
New graph presents these but need an inferential - maybe ANOVAs
\end{quote}

@@

>>>>

@@

We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}. We retained 41 work activity classifications which O*NET groups into categories of information input (5 statements; Where and how are the information and data gained that are needed to perform this job?), interacting with others (17 statements; What interactions with other persons or supervisory activities occur while performing this job?), mental processes (10 statements; What processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (9 statements; What physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Fifty-seven work context statements grouped into interpersonal relationships (14 statements; This category describes the context of the job in terms of human interaction processes), physical work conditions (30 statements; This category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (13 statements; This category involves the relationships or interactions between the worker and the structural characteristics of the job).

@@

\begin{quote}
Done - Figure \ref{fig:overallhist}
\end{quote}

\begin{quote}
NOT DONE: Combine current graphs 2 \(\rightarrow\) 8 into only 2 graphs (put resources, challenges, and demands on same graph; Kulas do this)
\end{quote}

@@

\begin{quote}
Done (at O*Net dimension level) - Table \ref{tab:cortab}.
\end{quote}

@@

\begin{quote}
Alicia can you present ``what this means'' and what is being presented in Figure \ref{fig:scalelevelgraphs} more clearly - also possibly add ANOVAs
\end{quote}

@@

\hypertarget{correlations}{%
\subsection{Correlations}\label{correlations}}

\begin{lltable}

\begin{TableNotes}[para]
\normalsize{\textit{Note.} The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)}
\end{TableNotes}

\small{

\begin{longtable}{lllllllllllllllllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:cortab}Challenge, hindrance, and resource bivariate correlations.}\\
\toprule
 & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:cortab} continued}}\\
\toprule
 & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
\midrule
\endhead
1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
2. onet.resource.mp & .61*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
3. onet.resource.wo & .46*** & .50*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
4. onet.resource.io & .49*** & .64*** & .45*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
5. onet.resource.ir & .46*** & .55*** & .37*** & .60*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
6. onet.resource.pc & .19*** & .15*** & .32*** & .18*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
7. onet.resource.sc & .43*** & .46*** & .41*** & .45*** & .48*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
8. onet.challenge.ii & .62*** & .49*** & .37*** & .41*** & .33*** & .08 & .33*** & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
9. onet.challenge.mp & .47*** & .63*** & .42*** & .50*** & .41*** & .09* & .38*** & .65*** & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
10. onet.challenge.wo & .34*** & .39*** & .64*** & .34*** & .30*** & .29*** & .38*** & .45*** & .49*** & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
11. onet.challenge.io & .34*** & .48*** & .33*** & .65*** & .48*** & .13** & .40*** & .50*** & .68*** & .43*** & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
12. onet.challenge.ir & .32*** & .40*** & .26*** & .48*** & .63*** & .23*** & .39*** & .46*** & .60*** & .39*** & .70*** & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
13. onet.challenge.pc & .12** & .08 & .21*** & .13** & .26*** & .66*** & .29*** & .14** & .12** & .33*** & .20*** & .31*** & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
14. onet.challenge.sc & .27*** & .31*** & .28*** & .38*** & .40*** & .27*** & .62*** & .36*** & .41*** & .38*** & .51*** & .45*** & .40*** & - &  &  &  &  &  &  & 3.66 & 0.59\\
15. onet.hindrance.ii & -.26*** & -.26*** & -.17*** & -.24*** & -.18*** & -.02 & -.08 & -.27*** & -.26*** & -.10* & -.19*** & -.16*** & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
16. onet.hindrance.mp & -.23*** & -.30*** & -.17*** & -.22*** & -.15*** & .05 & -.07 & -.22*** & -.27*** & -.10* & -.18*** & -.15*** & .12** & -.06 & .86*** & - &  &  &  &  & 2.10 & 1.05\\
17. onet.hindrance.wo & -.21*** & -.25*** & -.22*** & -.22*** & -.06 & -.02 & -.12** & -.14** & -.21*** & -.23*** & -.15*** & -.09* & .05 & -.10* & .66*** & .69*** & - &  &  &  & 2.31 & 1.02\\
18. onet.hindrance.io & -.22*** & -.27*** & -.14*** & -.29*** & -.18*** & -.01 & -.10* & -.21*** & -.25*** & -.10* & -.27*** & -.19*** & .07 & -.10* & .79*** & .86*** & .69*** & - &  &  & 2.23 & 1.03\\
19. onet.hindrance.ir & -.22*** & -.24*** & -.15*** & -.24*** & -.25*** & -.06 & -.11** & -.19*** & -.21*** & -.08* & -.20*** & -.23*** & .04 & -.12** & .79*** & .80*** & .61*** & .82*** & - &  & 2.35 & 0.89\\
20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16*** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38*** & .33*** & .47*** & .35*** & .47*** & - & 2.66 & 0.83\\
21. onet.hindrance.sc & -.13** & -.15*** & -.13** & -.19*** & -.13** & -.09* & -.23*** & -.12** & -.10* & -.05 & -.16*** & -.12** & -.01 & -.17*** & .62*** & .62*** & .56*** & .64*** & .66*** & .45*** & 2.64 & 0.80\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

\end{lltable}
